### 2025-01-06 README.Rmd
update scenarrios' maps and knit #53

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  out.width = "100%"
)
```
<!-- README.md is generated from README.Rmd. Please edit that file -->

@@

# biclar

@@

The goal of `biclar` is to store code and (in the releases) data for estimating cycling potential and influencing policy.

**biclar** is a tool for the design and assessment of different scenarios of the cycling network models in the Lisbon metropolitan area (LMA).

@@

-   Trips dataset with Origin and Destination, at *Freguesia* level, disaggregated by transport mode, from @IMOB  
-   [CAOP 2020](https://www.dgterritorio.gov.pt/cartografia/cartografia-tematica/caop?language=en) - Official limits of Portuguese areas.
-   Road network from [OpenStreetMap](https://www.openstreetmap.org/#map=11/38.7053/-9.1585)  
-   Main public transport interfaces at Lisbon Metro Region, provided by [Transportes Metropolitanos de Lisboa](https://www.tmlmobilidade.pt/)

@@

The baseline scenario makes use of the 2018 mobility survey data in LMA.  
We considered all trips between _Freguesias_.

@@

For the disagregation of OD pairs at _Freguesias_ level, we use [OD Jittering](https://github.com/atumworld/odrust) [@Jittering2022] method, which better suits walking and cycling trips modelling (shorter distances), instead of relying on centroids that concentrate all the trips between areas.

@@

#### ENMAC Scenario

See [here](region_enmac4_quiet.html) for full map.

```{r}
# knitr::include_url("m_rnet_enmac_region_fastest.html")
```

<iframe src="region_enmac4_quiet.html" width="800" height="400px" data-external="1">
</iframe>

See [here](articles/propotype.html) for results for each Municipality.

#### E-bike Scenario

<!-- todo -->

@@

<!-- todo -->

@@

# References {-}

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  out.width = "100%"
)
```

@@

# biclaR

@@

**biclaR** is a tool for the design and assessment of different scenarios of the cycling network models in the Lisbon metropolitan area (LMA).
The web application can be found at [u-shift.github.io/biclarwww](https://u-shift.github.io/biclarwww/).

**biclaR** is an open source project, see the source code on [github.com/U-Shift/biclar](https://github.com/U-Shift/biclar).

For a description of the methods and research underlying the project, see the [paper](https://www.sciencedirect.com/science/article/pii/S0198971524001595) "Reproducible methods for modeling combined public transport and cycling trips and associated benefits: Evidence from the biclaR tool" published in *Computers, Environment and Urban Systems* [@felix_reproducible_2025], and the methodological report [PT] on the [TML website](https://www.tmlmobilidade.pt/projetos-e-atividades/planos-e-estudos/rede-ciclavel-metropolitana-estudo-modelacao-e-ferramenta-de-apoio-ao-planeamento-e-decisao/).

@@

-   Trips dataset with Origin and Destination, at *Freguesia* level, disaggregated by transport mode, from @IMOB\
-   [CAOP 2020](https://www.dgterritorio.gov.pt/cartografia/cartografia-tematica/caop?language=en) - Official limits of Portuguese areas.
-   Road network from [OpenStreetMap](https://www.openstreetmap.org/#map=11/38.7053/-9.1585)\
-   Main public transport interfaces at Lisbon Metropolitan Area, provided by [Transportes Metropolitanos de Lisboa](https://www.tmlmobilidade.pt/)

@@

The baseline scenario makes use of the 2018 mobility survey data in LMA.\
We considered all trips between *Freguesias*.

@@

For the disagregation of OD pairs at *Freguesias* level, we use [OD Jittering](https://github.com/atumworld/odrust) [@Jittering2022] method, which better suits walking and cycling trips modelling (shorter distances), instead of relying on centroids that concentrate all the trips between areas.

@@

#### ENMAC Scenario up to 5km

See [here](https://u-shift.github.io/biclarwww/aml/mapa_cenario1.html) for full map.

<iframe src="https://u-shift.github.io/biclarwww/lisboa/mapa_cenario1.html" width="800" height="400px" data-external="1">

</iframe>

See [here](https://u-shift.github.io/biclarwww/) for results for each Municipality.

#### ENMAC Scenario up to 10km (E-bike)

See [here](https://u-shift.github.io/biclarwww/aml/mapa_cenario2.html) for full map.

<iframe src="https://u-shift.github.io/biclarwww/lisboa/mapa_cenario2.html" width="800" height="400px" data-external="1">

</iframe>

@@

See [here](https://u-shift.github.io/biclarwww/aml/mapa_cenario3.html) for full map.

<iframe src="https://u-shift.github.io/biclarwww/lisboa/mapa_cenario3.html" width="800" height="400px" data-external="1">

</iframe>

@@

# References {.unnumbered}
